% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jiaye Fang}
\name{(Oscar)}

\basicInfo{
  (530) 760-9441 $\bullet$
  \href{mailto:oscar.fang@gwmail.gwu.edu}{oscar.fang@gwu.edu} $\bullet$
  \href{https://github.com/cjsrxzdyzds}{GitHub} $\bullet$
  \href{https://www.linkedin.com/in/oscarfang/}{Linkedin}
}

\section{Education}
\datedsubsection{\textbf{\href{https://www.gwu.edu/}{The George Washington University}}, School of Engineering \& Applied Science}{District of Columbia}
\datedsubsection{\textit{Master of Science in Data Analytics (Computer Science Track)}}{08/2023 -- 05/2025(excepted)}

\datedsubsection{\textbf{\href{https://www.ucdavis.edu/}{University of California, Davis}}, College of Letters \& Science}{Davis, California}
\datedsubsection{\textit{Bachelor of Science in Computer and Information Science}}{09/2018 -- 12/2021}
\begin{itemize}
    \item \underline{{\href{https://catalog.ucdavis.edu/courses-subject-code/}{Relevant Coursework}}}: Linear Algebra, Optimization, Probability \& Statistical Modeling for Computer Science, Artificial Intelligence, Algorithms Design \& Analysis, Development in Unix \& C/C++, Database System.
\end{itemize}

\section{Research Experience}
\datedsubsection{\textbf{\href{https://www.first-imaging.com/en/}{First Imaging Lab}}, Cooperation with \href{https://www.sjtu.edu.cn/}{Shanghai Jiao Tong University}}{Shanghai, China}
\datedsubsection{Machine Learning Engineer}{09/2022 -- 04/2023}
\begin{itemize}
\item Orchestrated the development of an in-house pipeline tailored for the automated calculation and continuous monitoring of signal-noise ratio (SNR) in medical images, leading to a substantial optimization of our data pipeline processes and heightened operational efficiency.
\item Contributed significantly to the evolution of medical imaging technology by conducting in-depth research into the three-dimensional reconstruction of medical images. This endeavor entailed an exhaustive review of the latest literature in the field and the meticulous reproduction of existing implementations, all executed using Matlab.
\item Demonstrated exceptional attention to detail by skillfully aligning medical images with 3-D models utilizing the Insight Toolkit (ITk). Following this alignment, harnessed the power of convolutional neural networks (CNNs) within the PyTorch framework to elevate the performance of models, reinforcing our unwavering commitment to excellence in healthcare technology.
\end{itemize}

%\datedsubsection{\textbf{\href{https://www.blocbox.io/}{BlocBox Research}}, member of \href{https://directory.singaporefintech.org/directory/listing/blocbox}{Singapore FinTech Association}}{Remote}
%\datedsubsection{Data Scientist}{05/2021 -- 08/2021}
%\begin{itemize}
%\item Developed a web crawler via Python selenium packages to collect discussions and textual data from Reddit on cryptocurrencies 
%\item Conducted cluster analysis and applied unsupervised machine learning techniques such as K-means clustering to classify existing and novel cryptocurrencies
%\item Verified the classification accuracy performed by existing models by themes, price co-movement, token velocity, and P/S ratio
%\item Tested thematic trading strategies with cryptocurrencies by using historical and real-time data, providing recommendations on potential improvement
%\end{itemize}

\section{Selected Academic Projects}
\datedsubsection{\textbf{Credit Card Anti-Fraud System (C++)}, Project Lead}{04/2021 -- 08/2021}
\begin{itemize}
  \item Engineered a concurrent web server capable of seamlessly providing authentication services to more than 1000 simultaneous clients, effectively managing network traffic to prevent overload.
  \item Transformed a non-concurrent web server into a multi-threaded system, enabling it to efficiently handle multiple requests concurrently, boosting overall responsiveness.
  \item  Designed and implemented a dynamic scheduling policy for optimizing HTTP request allocation to waiting worker threads, resulting in enhanced resource utilization and faster response times.
  \item Spearheaded the development of a robust verification service, an integral component of an experimental credit card anti-fraud system, contributing to heightened security and fraud prevention measures.
\end{itemize}

\datedsubsection{\textbf{Golang Implementation of HTTP Proxy (Golang)}, Project Lead}{04/2020 -- 01/2021}
\begin{itemize}
  \item Initiated the development and successful deployment of a robust tunnel connection system, utilizing the CONNECT method within the HTTP/1.1 protocol. This innovation significantly bolstered the efficiency and security of data transfers, enabling seamless communication between clients and servers.
  \item Engineered an advanced proxy solution purpose-built for the efficient handling of HTTPS requests. Distinguished by its lean architecture, this proxy eliminates the need for content parsing or forwarding. This not only optimizes resource utilization but also reinforces data privacy and security, underscoring my dedication to creating streamlined and secure web technologies.
  \item Played a pivotal role in enhancing streaming services for live gaming platforms. Through the optimization of data delivery mechanisms, these platforms achieved consistent and uninterrupted streaming experiences for gamers. This achievement not only boosted user satisfaction but also fostered the growth and engagement of the gaming community, highlighting my commitment to delivering superior technological solutions.
\end{itemize}

% \datedsubsection{\href{http://ml.cs.tsinghua.edu.cn/}{\textbf{Statistical AI \& Learning (TSAIL) Group}}, Tsinghua University}{Beijing, China}
% \datedsubsection{Research Assistant}{03/2018 -- 08/2020}
% \begin{itemize}
% \item Ranked the first place in VizDoom AI Competition 2018, passing 8 out of 10 tasks far exceeding the second place which only passed 4 tasks, by proposing an environment-aware hierarchical reinforcement learning algorithm, which was accepted by IJCAI'19
% \item Implemented an elegant, light-weighted deep reinforcement learning library \href{https://github.com/thu-ml/tianshou}{Tianshou} with 3.5k GitHub stars
% \end{itemize}

%\datedsubsection{\textbf{\href{http://mila.quebec/en}{Montreal Institute for Learning Algorithms (MILA)}}}{Montréal, QC}
%\datedsubsection{Research Assistant, Advisor: Prof. \href{https://mila.quebec/en/yoshua-bengio/}{Yoshua Bengio}}{07/2019 -- 10/2019}
%\begin{itemize}
    %\item Proposed \textit{Rule-Transformer} for better disentanglement and out-of-distribution generalization
    %\item Evaluated in a wide range of tasks from machine translation to multitask imitation learning
%\end{itemize}

%\datedsubsection{\textbf{\href{https://www.sensetime.com/en}{Sensetime Inc.}}}{Beijing, China}
%\datedsubsection{Research Intern}{03/2018 -- 06/2018}
%\begin{itemize}
    %\item Designed and optimized a temporal and spatial domain-based noise reduction network
    %\item Generated high-quality results in about 70ms given eight 12M pixel full-resolution images on a GTX1060
%\end{itemize}

%\section{Selected Awards}
%\begin{itemize}
    %\item Outstanding Graduates (top 10\%)\hfill 2020
    %\item Comprehensive Excellence Award (top 5\%)\hfill 2018
    %\item 1st place, VizDoom AI Competition [\href{http://vizdoom.cs.put.edu.pl/competitions/vdaic-2018-cig/results}{Official Result}] [\href{https://www.jiqizhixin.com/articles/2018-08-23-12}{Post in Chinese}]\hfill 2018
    %\item Bronze Prize, National Olympiad in Infomatics (NOI)\hfill 2015
%\end{itemize}

%\section{Publications}
%\begin{itemize}
    %\item Shihong Song*, \textbf{Jiayi Weng}*, Hang Su, Dong Yan, Haosheng Zou, and Jun Zhu, ``Playing FPS Game with Environment-aware Hierarchical Reinforcement Learning,'' in \textbf{IJCAI'19 (oral)}, \href{https://trinkle23897.github.io/cv/viz2018.html}{[Page]} \href{https://www.ijcai.org/proceedings/2019/0482.pdf}{[PDF]}
    %\item \textbf{Jiayi Weng}, Tsung-Yi Ho, Weiqing Ji, Peng Liu, Mengdi Bao, and Hailong Yao,  ``URBER: %Ultrafast Rule-Based Escape Routing Method for Large-Scale Sample Delivery Biochips,'' in \textbf{TCAD'18}, \href{https://trinkle23897.github.io/cv/urber.html}{[Page]} \href{https://ieeexplore.ieee.org/document/8552446}{[PDF]}
%\end{itemize}

\section{Skills}
\textbf{Programming Languages:} \small Python, C/C++, JavaScript, Java, HTML/CSS, PHP, Bash (ranked by proficiency)

\textbf{Tools and Frameworks:} \small Git, \LaTeX, PyTorch, Spark, Docker, React, Bootstrap

\textbf{Languages:} \small Mandarin (Native), English (Proficient)


\end{document}
